Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-12-05 paper-proposal.tex
STOP: copy and pasting

\begin{document}
%contain, at the top, the following affirmative statement. "This website is free and open to all users and there is no login requirement." Additionally, any third party software employed by the website that has more restrictive usage terms must be listed.
This website is free and open to all users and there is no login requirement. The code for this webserver and all third party software used by this website is available under the open-source Apache 2.0 or BSD 3-clause licenses.

% include the website address; website name; and the names, affiliations, and email addresses of all authors.

>>>>

\begin{document}
%contain, at the top, the following affirmative statement. "This website is free and open to all users and there is no login requirement." Additionally, any third party software employed by the website that has more restrictive usage terms must be listed.
This website is free and open to all users and there is no login requirement. The code for this webserver and all third party software used by this website are available under the open-source Apache 2.0 or BSD 3-clause licenses.

% include the website address; website name; and the names, affiliations, and email addresses of all authors.
The website is available at \url{https://lfz.corefacility.ca/superphy/spfy/}. Spfy's codebase is provided at \url{https://github.com/superphy/backend} and a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.
